HealpixNet: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2018-08-31 scnn.tex
an HEALPix => a HEALPix

\begin{figure}
    \centering
    \includegraphics[height=7em]{sphere_grid_equirectangular}
    \hfill
    \includegraphics[height=7em]{sphere_grid_cubedsphere}
    \hfill
    \includegraphics[height=7em]{half_graph_4}
    \caption[]{Some pixelizations of the sphere. Left: the equirectangular grid, using equiangular spacing in a standard spherical-polar coordinate system. Middle: an equiangular cubed-sphere grid, as described in \citep{ronchi1996cubed}. Right: graph built from an HEALPix pixelization of half the sphere ($N_{side} = 4$). By construction, each node has 8 neighbors, except the highlighted ones which have only 7.\footnotemark[7] Left and middle figures are taken from \citep{boomsma2017spherical}.}
    \label{fig:sphere_grids}
    \label{fig:healpix_graph_4}
\end{figure}

@@

The performance of HealpixNet is demonstrated on a discrimination problem: the classification of convergence maps into two cosmological model classes.
The experiment presented here is similar to the one by \citep{schmelze2017cosmologicalmodel}.
These maps are similar to those created with gravitational lensing techniques \citep{chang2017curvedsky}.
The two sets of maps were created using the standard cosmological model with two sets of cosmological parameters.
The classification methods were trained to predict a label from an HEALPix map.
Both our Python implementation\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}} and the data\footnote{\url{https://doi.org/10.5281/zenodo.1303272}} to reproduce those experiments are openly available online. Furthermore, Jupyter notebooks demoing the method and problem can be run from your browser without installing anything.

>>>>

\begin{figure}
    \centering
    \includegraphics[height=7em]{sphere_grid_equirectangular}
    \hfill
    \includegraphics[height=7em]{sphere_grid_cubedsphere}
    \hfill
    \includegraphics[height=7em]{half_graph_4}
    \caption[]{Some pixelizations of the sphere. Left: the equirectangular grid, using equiangular spacing in a standard spherical-polar coordinate system. Middle: an equiangular cubed-sphere grid, as described in \citep{ronchi1996cubed}. Right: graph built from a HEALPix pixelization of half the sphere ($N_{side} = 4$). By construction, each node has 8 neighbors, except the highlighted ones which have only 7.\footnotemark[7] Left and middle figures are taken from \citep{boomsma2017spherical}.}
    \label{fig:sphere_grids}
    \label{fig:healpix_graph_4}
\end{figure}

@@

The performance of HealpixNet is demonstrated on a discrimination problem: the classification of convergence maps into two cosmological model classes.
The experiment presented here is similar to the one by \citep{schmelze2017cosmologicalmodel}.
These maps are similar to those created with gravitational lensing techniques \citep{chang2017curvedsky}.
The two sets of maps were created using the standard cosmological model with two sets of cosmological parameters.
The classification methods were trained to predict a label from a HEALPix map.
Both our Python implementation\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}} and the data\footnote{\url{https://doi.org/10.5281/zenodo.1303272}} to reproduce those experiments are openly available online. Furthermore, Jupyter notebooks demoing the method and problem can be run from your browser without installing anything.
